---
title: "cross_validation"
author: "Hana Akbarnejad"
date: "11/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(modelr)
library(tidyverse)
library(mgcv)
```

**Cross Validation = Model Selection!**

model complexity

accuracy

prediction power for future datset

```{r}

nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + theme_bw()
```

Training and Testing
```{r}

train_df = sample_frac(nonlin_df, size = .8)
test_df = anti_join(nonlin_df, train_df, by = "id")   # new join! in "nonlin_df" dataset, give me anything not                                                               apperaed in "train_df"

ggplot(train_df, aes(x = x, y = y)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red")
```

Fit three models with different goodness:

```{r}

linear_mod = lm(y ~ x, data = train_df)
smooth_mod = mgcv::gam(y ~ s(x), data = train_df)
wiggly_mod = mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```

Looking at some fits:
```{r}
train_df %>% 
  add_predictions(linear_mod) %>% 
    ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")

train_df %>% 
  add_predictions(smooth_mod) %>% 
    ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")

train_df %>% 
  add_predictions(wiggly_mod) %>% 
    ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")
```

Try to do croos_validation: use Root Mean Sqyared Error!
```{r}

rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```

Now, we can do all this using modelr package:

```{r}

cv_df = crossv_mc(nonlin_df, 100)                  # creats two new list columns: train and test - 80/20 is default!

# we can pull these datasets and work with them:
cv_df %>% pull(train) %>% .[[1]] %>% as_tibble

# doing the same, but in a non-merory_efficient way!
cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

Trying to fit the linar model to all of these!!!
```{r}

cv_df %>% 
  mutate (
    linear_mods = map (.x = train, ~ lm(y ~ x, data = .x)),
    rmse_lin = map2(.x = linear_mods, .y = test, ~ rmse(.x, .y))
  )

# doing the same things for different models:
cv_df = 
  cv_df %>% 
  mutate(linear_mod  = map(train, ~lm(y ~ x, data = .x)),
         smooth_mod  = map(train, ~mgcv::gam(y ~ s(x), data = .x)),
         wiggly_mod  = map(train, ~gam(y ~ s(x, k = 30), sp = 10e-6, data = .x))) %>% 
  mutate(rmse_linear = map2_dbl(linear_mod, test, ~rmse(model = .x, data = .y)),
         rmse_smooth = map2_dbl(smooth_mod, test, ~rmse(model = .x, data = .y)),
         rmse_wiggly = map2_dbl(wiggly_mod, test, ~rmse(model = .x, data = .y)))
```

Visulaizing this:
```{r}

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

# Now work on an example:
```{r}

#data import and visualize

child_growth = read_csv("./data/nepalese_children.csv")

child_growth %>% 
  ggplot(aes(x = weight, y = armc)) + 
  geom_point(alpha = .5)
```

```{r}

```

